Spike-and-Slab Generalized Additive Models and Scalable Algorithms for High-Dimensional Data

### 2022-02-11 Manuscript/R&R/01-reviewer_1.Rmd
Update response

__Response__:

>>>>

__Response__: We don't think any preliminary checkings or testings are necessary before implementing the proposed model, as long as some general rules of thumb for high-dimensional modeling are followed. Such rules of thumb includes .[Insert citaiton for ultra high-dimension thing, as the number of predictors is a function of the sample size.] As a supporting evidence, our added simulation demonstrates the proposed model performs well, in reference to the linear lasso model, even when signals are linear and sparse (see response to the Comment 1).

We acknowledge the reviewer's comment that careful deliberation are necessary when conducting analysis, which includes domain knowledge. However, the discussion of modeling strategy, e.g. starting with more flexible models or linear models, or using statistical testings to examine assumptions, is out of the scope of the current manuscript. The current manuscript focuses on introducing a novel model that allows flexibility when modeling complex signals.
